### 2016-08-22 ms/ms.tex
added bits to the discussion

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible, even though two changing points did occur in the non assembling hedgerow six between 2009 and 2010, and 2010 and 2011 (HR6, Fig.~\ref{fig:changePoints}) . Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

Given that changing ponts did occur, TRANSITION... Surprisingly, the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence.  For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were also the
only species that changed what module (i.e., community) they were
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be best able to exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

%% node/species turnover

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, generalist core \cite{albrecht2010plant}. With preferential
attachment, however, we would also expect connectance and
specialization to increase, and see no such trends. The stable level
of network-level specialization through the assembly process may be
due to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation -- providing further
evidence that hedgerows are valuable tool for promoting species
conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
time it takes for a perturbation to spread through a network, as
measured by algebraic connectivity, is correlated with species
richness, the increase and plant and pollinator richness following
restoration is at least partially responsible for enhancing network
robustness. SOMETHING ABOUT DIVERSITY AND STABILITY

>>>>

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible, even though two changing points did occur in the non assembling hedgerow six between 2009 and 2010, and 2010 and 2011 (HR6, Fig.~\ref{fig:changePoints}). Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

Given that changing ponts did occur, we then turned to explore how these changing points came to be, and what species were responsible for it. Ecolgical theory predicts that species abundance is positively correlated to number of interaction partners a species has (degree \citep{Bluthgen2007}). Thus, we expected that the more abundant species would be more persisten through network assembly, and would contribute the least to the changing points. Surprisingly however, we encountered the opposite: the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence. For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were the
only species that changed what module (i.e., community), and they were also 
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be able to better exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources available, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

%% node/species turnover  - I am not sure I get these results so there might be some nonsense in the below paragraph...
Given the regional species pool it is possible that specialization migth be constant either because species are not changing through time, or because there is a species turnover, but new species have the same role/posotion as the species there are absent in the following time step. We found that node turover was higher in assembling and non-assembling hedgerows when compared to field margin, but there was no difference between them. Thus, maybe looking just at network level metrics, such as nestedness and modularity, when exploring the temporal assembly of ecological networks might be misleading, given that there is a node turnover happening at the species level.

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, pre existing generalist core \cite{albrecht2010plant}. With preferential
attachment, however, we would also expect connectance and
specialization to increase, and we found no such trends. The stable level
of network-level specialization through the assembly process may be
due to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation -- providing further
evidence that hedgerows are valuable tool for promoting species
conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
vulnerability of the network to cascading effects, as
measured by algebraic connectivity, is correlated with species
richness, the increase and plant and pollinator richness following
restoration is at least partially responsible for enhancing network
robustness to cascading effects. This result contributes to the stability and diversity debate indicating that diversity might promote statibility, even though there are contrasting results in the literature \citep [e.g.][]{may1972will, pimm1984complexity, montoya2006ecological}. However, the robustness of ecological communities to disturbances  might depend on the identity of the species mostly being affected by the disturbance (REF). For example, networks might be more sensible to the disturbance of a generalist when compared to a specialist (REF).
